Population Inference of Eccentric Binary Black Holes

### 2023-05-23 paper/paper.tex
Updates from Overleaf

\begin{align}
\label{eq:plawg}
p(m_1,m_2,e) = &C(\alpha,k_m,m_{min},m_{max},M_{max},e)  
\nonumber \\ & \frac{(\frac{m_2}{m_1})^{k_m}m_1^{-\alpha}}{(m_1-m_{min})\sigma_e} 
\nonumber \\ &
\sqrt{\frac{2}{\pi}} e^{(-1/2)(e/\sigma_e)^2}
\end{align}
We use $k_m=0$, because GW networks are much more senstive to more massive BHs with $M\geq 200 M_\odot$

@@

>>>>

\begin{align}
\label{eq:plawg}
p(m_1,m_2,e) = &C(\alpha,k_m,m_{min},m_{max},M_{max},e)  
\nonumber \\ & \frac{(m_2/m_1)^{k_m}m_1^{-\alpha}}{(m_1-m_{min})\sigma_e} 
\nonumber \\ &
\sqrt{\frac{2}{\pi}} e^{(-1/2)(e/\sigma_e)^2}
\end{align}
We use $k_m=0$, because GW networks are much more senstive to more massive BHs with $M\geq 200 M_\odot$

@@

\section{Inference of Synthetic BBH Population}
We have generated two distinct populations consistent of $100$ BBH by fixing the power law model parameter $\Lambda$ given in Eq. \ref{eq:plaw}. 
The parameters $\alpha=-2$, $m_{min}=10$, $m_{max}=50$ are same for both populations. The only difference between two generated populations is the dispersion of $\sigma_e$. The range for the first populations is $0<\sigma_e<0.5$ and for the second one is $0<\sigma_e<0.38$.
Furthermore, to make the comparison of the eccentric population with non-eccentric, we have created two more different populations by scaling already generated two populations by using the Eq. \ref{eq:scaling}. The Eq. \ref{eq:scaling} removes the eccentric component from the population, scales the masses and eventually we get non-eccentric population.
\begin{align}
\label{eq:scaling}
M^{ecc} = \frac{M}{(1-\frac{157}{24}e^2)^{3/5}}
\end{align}

\subsection{First Population: $0<\sigma_e<0.5$}
The following is the figure which shows the

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop3d05.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop2d05.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop2d05scl.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}
\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop2d05diff.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}
\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss05.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\subsection{Second Population: $0<\sigma_e<0.38$}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}
